{\bf A Review on Recent Advances in Unsupervised Relation Extraction} \\ \it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal

### 2013-07-19 term-paper/paper.tex
Modified: LDA

\title{{\bf An Introduction on Recent Advances in Unsupervised Relation Extraction} \\
\it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal}
\author{ {\bf Ehsan Khoddammohammadi}  \\
Faculty of Computational Linguistics \\
Saarland University\\
{\small ehsank@coli.uni-saarland.de}
}
\date{\today}

\begin{report}
\pagestyle{plain}
\pagenumbering{roman}
\maketitle

@@

The aim of this paper is to review recent and influential methods on
Unsupervised Relation Extraction. In the first part, the definition and a general background
for relation extraction task is provided which identifies important aspects and
difficulties of the task. In the second part, five major previous works are
briefly reviewed. An extra section will be dedicated to a weakly supervised method, distant supervision, which is 
necessary due to its impact on recent advances in the task. And
finally in the last part, the paper will be concluded by comparing the discussed methods.

@@

\subsection{Input format and preprocessing}
\label{ch:input}
Authors have chosen a subset of New York Times articles from year 2000 to 2007 which parts with
abnormal style of writing like obituary content or hard structures to deal like lists are filtered out.
They have done several pre-processing steps:
\begin{enumerate}
\item Tokenization
\item Sentence split
\item POS tagging (all last three steps with Stanford tools)
\item Named entity tagging (Finkel2005)
\item Dependency parsing (MaltParser)
\end{enumerate}
Among all dependency paths we are just interested in those which link two named entities.
 So basically we are hopeful that realization of one relation is available somewhere in this 
 path most likely as a verb which relates two mentioned named entities. We collect these kinds of 
 paths and based on some conditions that we have already discussed in ??? DIRT we filter out non-important links.

@@

\subsection {Model Description}
\label{ch:model}

@@

\section{Summaru}
\label{ch:conclusion}

>>>>

\title{{\bf A Review on Recent Advances in Unsupervised Relation Extraction} \\
\it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal}
\author{ {\bf Ehsan Khoddammohammadi}  \\
Faculty of Computational Linguistics \\
Saarland University\\
{\small ehsank@coli.uni-saarland.de}
}
\date{\today}

\begin{document}
\pagestyle{plain}
\pagenumbering{roman}
\maketitle

@@

The aim of this paper is to review recent and influential methods on
Unsupervised Relation Extraction. In the first chapter, the definition and a general background
for relation extraction task is provided which identifies important aspects and
difficulties of the task. In the second chapter, five major previous works are
briefly reviewed. The third chapter is dedicated to a weakly supervised method, distant supervision, which is 
necessary due to its impact on recent advances in the task. And
finally in the last chapter, the paper will be concluded by comparison of discussed methods and important lessons learned from each of them.

@@

\subsection{Input format and preprocessing}
\label{ch:input}
Authors have chosen a subset of New York Times articles from year 2000 to 2007 which some of its parts with
abnormal style of writing like obituary content are filtered out.
They have done several pre-processing steps:
\begin{enumerate}
\item Tokenization
\item Sentence split
\item POS tagging (?? all last three steps with Stanford tools)
\item Named entity tagging ( ?? Finkel2005)
\item Dependency parsing (??MaltParser)
\end{enumerate}
Among all dependency paths they are just interested in those which link two named entities.
 Authors assume that realization of one relation is available in this 
 path most likely as a verb which relates two mentioned named entities. These types of 
 paths are collected and based on some conditions that we have already discussed in (??? DIRT), non-important links are filtered out.

@@

\subsection {Model Description}
\label{ch:model}
All the three models in this work are generative models. Generative models are jointly modeling hidden variables and observable variables and 
are in contrast to discriminative models. For more information on generative models please see ?? and ??.\\

\textbf{Rel-LDA} is the first model proposed in (?? Yao). 
In this model, features, $f$, are generated from a distribution , $\Phi_{rf}$. Each type
 of relation is represented with a binary indicator variable, $r$. Each document is a mixture of few relations
  and relations are generated from a multinomial distribution $\Theta_{doc}$. $\Theta_{doc}$ is a distribution
  of relations for a specific document and can be shown as $P(r|doc)$. By choosing a right prior distribution for $\Theta$
   and $\Phi$ we can impose an assumption that any document contains a few number of relation types. 
   Another advantage of having prior is that it helps to avoid overfitting. Dirichlet prior with small parameter $\alpha$ is 
   chosen for this purpose in the paper. For more on the role of priors and specially Dirichlet prior
    please read ?? and ??.
    Rel-LDA is decribed with a graphical model in figure ???.
    Shaded circles are showing the observable variables and other circles are hidden variables except 
    the priors which are set by ourselves. The direction of arrow shows the dependency in this sense 
    that destination node (variable) is dependent on source node.

    Features or observable variables in Rel-LDA are:
    \begin{itemize}
      \item The dependency path
      \item Source of the path (the first named entity)
      \item Destination of the path (the second named entity)
    \end{itemize}

   	An exact sampling method called \emph{variational inference} is used by authors to compute 
   	the posterior distribution of the model, $P(r|f)$.
   	After learning, we will have clusters of relation types which each instance of a specific cluster 
   	is a relation that is supposed to be semantically equivalent to the other members of this cluster.
   	\\

   	In the second model, \textbf{Rel1-LDA},The only difference is that  more features are used in the learning procedure.
   	 The idea is that using more features could be useful as tie-breakers and also discriminators between instances
   	  to make new clusters. With direct reference to the paper, the authors believe that more features 
   	  lead to better refinement of clusters. We will see later that this assumption holds in practice.
   	   The new features that they have introduced in this new model are:
   	   \begin{itemize}
   	     \item Trigger: Any word in a dependency path except than stop words. 
   	     \item Part of speech sequence: The sequence of pos tags of a dependency path. 
   	     \item Named entity pair: The type of source and destination named entity. 
   	   \end{itemize}

 Among all the newly introduced features, NE pair is the most interesting one which leads to a 
 significant observation that the third model will try to address that. Authors observed that 
 Rel-LDA will put these three relations in one cluster because the second argument of all of them is location:

 \begin{enumerate}
   \item \emph{ X was born in Y}
   \item \emph{ X lives in Y}
   \item \emph{ X, a company in Y}
 \end{enumerate}

 While the first argument in the first two relations refers to a PER, the first argument of the 
 third relation is an instance of ORG type. By using NER pairs as feature we can split this cluster 
 to two clusters with respect to basic types of NE in relations arguments. 
 This observation leads us to invest more on type identification of arguments to have more pure 
 clusters and is the main focus of the third model, \textbf{Type-LDA}.

 Selectional preferences of a relation are constraint over possible arguments for the relation.
  Basically, any relation only accepts a few number of entity types and this could be an important constraint
   for inducing relations. Relations of each cluster should have similar selectional preferences and
    accept same entity types. Type-LDA is proposed for this reason, it will induce entity types 
    and relation clusters jointly to benefit more from selectional preferences of relations.

@@

\section{Summary}
\label{ch:conclusion}
